---
title: "Lesotho's Basotho Wool Trade, 2010-2024"
author: "Kyeesha M. Wilcox"
date-modified: today
format:
  dashboard:
    scrollable: true
    theme: united #view others: https://bootswatch.com/
    nav-buttons: 
    - icon: linkedin
      href: https://www.linkedin.com/in/kyeesha-wilcox-a84a36251
      aria-label: LinkedIn
---

```{r}

#----import libraries
library(tidyverse)
library(DT)
library(gt)
library(formattable)
library(plotly) #interactive visualizations
library(sf) #for maps
library(RColorBrewer) #for map color schemes
library(scales)

#----import data
b_wool_2v <- read.csv("https://raw.githubusercontent.com/wilcox-km/lesotho-basotho-wool/refs/heads/main/data/cleaned_basotho_wool.csv")

data_dict <- read.csv("https://raw.githubusercontent.com/wilcox-km/lesotho-basotho-wool/refs/heads/main/data/cleaned_data_dictionary.csv")


#for the maps----

merged_world <- read.csv("https://raw.githubusercontent.com/wilcox-km/lesotho-basotho-wool/refs/heads/main/data/merged_world.csv")
merged_valid <- read.csv("https://raw.githubusercontent.com/wilcox-km/lesotho-basotho-wool/refs/heads/main/data/merged_valid.csv")
merged_na <- read.csv("https://raw.githubusercontent.com/wilcox-km/lesotho-basotho-wool/refs/heads/main/data/merged_na.csv")


#for the heat map----

merged_all <- read.csv("https://raw.githubusercontent.com/wilcox-km/lesotho-basotho-wool/refs/heads/main/data/merged_allyrs_allcountries.csv")
china <- read.csv("https://raw.githubusercontent.com/wilcox-km/lesotho-basotho-wool/refs/heads/main/data/china_allyrs.csv")
india <- read.csv("https://raw.githubusercontent.com/wilcox-km/lesotho-basotho-wool/refs/heads/main/data/china_allyrs.csv")
south_africa <- read.csv("https://raw.githubusercontent.com/wilcox-km/lesotho-basotho-wool/refs/heads/main/data/south_africa_allyrs.csv")            
uruguay <- read.csv("https://raw.githubusercontent.com/wilcox-km/lesotho-basotho-wool/refs/heads/main/data/uruguay_allyrs.csv")


#for the takeaways----

importer <- read.csv("https://raw.githubusercontent.com/wilcox-km/lesotho-basotho-wool/refs/heads/main/data/importer.csv")
top_year <- read.csv("https://raw.githubusercontent.com/wilcox-km/lesotho-basotho-wool/refs/heads/main/data/top_year.csv")
most_revenue <- read.csv("https://raw.githubusercontent.com/wilcox-km/lesotho-basotho-wool/refs/heads/main/data/most_revenue.csv")
busy_season <- read.csv("https://raw.githubusercontent.com/wilcox-km/lesotho-basotho-wool/refs/heads/main/data/busy_season.csv")

```

# Map

::::::: {layout-ncol="2"}
::: panel-tabset
### Net Weight (kg)

```{r}

# light grey boundaries
l <- list(color = toRGB("gray"), width = 0.5)

# specify map projection/options
g <- list(
  showframe = FALSE,
  showcoastlines = FALSE,
  showland = TRUE,
  landcolor = toRGB("gray"),
  showcountries = TRUE,
  countrycolor = toRGB("gray"),
  projection = list(type = 'Winkel-Tripel')
)

#visualize and animate map

fig <- plot_ly(
  data = merged_world, 
  type ='choropleth', 
  locations=merged_world$CODE,
  frame = ~year, # for animation
  showscale = TRUE,
  colorbar = list (
      title = list(text = 'Total Net Weight (kg)')
    )
  )

fig <- fig %>%
  #base map (to fill in missing regions with gray area)
  add_trace(
    data = merged_world,
    type = "choropleth",
    locations = ~CODE,
    z = rep(1, nrow(merged_world)), #dummy constant value to force fill
    colorscale = list(c(0, "gray"), c(1, "gray")),
    marker = list(line = list(color = toRGB("black"), width = 0.5)),
    showscale = FALSE, #hide dummy legend
    hoverinfo = "text",
    text = ~paste(COUNTRY, ": No Data")
  ) %>%
#main data
  add_trace(
    data = merged_valid,
    type = "choropleth",
    locations = ~CODE, 
    marker = list(line = l),
    z = ~total_netwgt_kgs, 
    color = ~total_netwgt_kgs, 
    colorscale = 'RdPu',
    text = ~country
  )

fig <- fig %>% layout(
  title = list(
    text = 'Total Net Weight by Country',
    y = 0.95), #adjusts vertical position (0 to 1)
  geo = list(
    scope = "world",
    #landmass basemap
    showland = TRUE,
    landcolor = toRGB("gray50"), # changes the color of valid countries with no data
    #ocean basemap
    showocean = TRUE,
    oceancolor = toRGB("lightblue")
  )
)

fig

```

### Revenue (USD $)

```{r}

# light grey boundaries
l <- list(color = toRGB("grey"), width = 0.5)

# specify map projection/options
g <- list(
  showframe = FALSE,
  showcoastlines = FALSE,
  showland = TRUE,
  landcolor = toRGB("gray"),
  showcountries = TRUE,
  countrycolor = toRGB("gray"),
  projection = list(type = 'Winkel-Tripel')
)

#visualize and animate map

fig <- plot_ly(
  data = merged_world, 
  type ='choropleth', 
  locations=merged_world$CODE,
  frame = ~year, # for animation
  showscale = TRUE,
  colorbar = list (
    title = list(text = 'Total Revenue (USD $)')
  )
)

fig <- fig %>%
  #base map (to fill in missing regions with gray area)
  add_trace(
    data = merged_world,
    type = "choropleth",
    locations = ~CODE,
    z = rep(1, nrow(merged_world)), #dummy constant value to force fill
    colorscale = list(c(0, "gray"), c(1, "gray")),
    marker = list(line = list(color = toRGB("black"), width = 0.5)),
    showscale = FALSE, #hide dummy legend
    hoverinfo = "text",
    text = ~paste(COUNTRY, ": No Data")
  ) %>%
  #main data
  add_trace(
    data = merged_valid,
    type = "choropleth",
    locations = ~CODE, 
    marker = list(line = l),
    z = ~total_value_usd, 
    color = ~total_value_usd, 
    colorscale = 'RdPu',
    text = ~country
  )

fig <- fig %>% layout(
  title = list(
    text = 'Total Revenue by Country and Year',
    y = 0.95), #adjusts vertical position (0 to 1)
  geo = list(
    scope = "world",
    #landmass basemap
    showland = TRUE,
    landcolor = toRGB("gray50"), # changes the color of valid countries with no data
    #ocean basemap
    showocean = TRUE,
    oceancolor = toRGB("lightblue")
  )
)

fig
  
```
:::

::::: panel-tabset
### Net Weight (kg)

::: panel-tabset
#### All

```{r}
#| title: All

# level order so Jan is at the beginning of the y-axis
merged_all <- merged_all %>%
  mutate(month_abb = factor(merged_all$month_abb, levels = c("Jan", "Feb", "Mar", "Apr", "May", "Jun", "Jul", "Aug", "Sep", "Oct", "Nov", "Dec")))

p <- ggplot(merged_all, aes(x=month_abb, y=year)) +
  geom_tile(aes(fill = net_wgt_kgs)) +
  scale_fill_distiller(palette = "RdPu", direction = 1 ,labels = comma) +
  scale_y_reverse(breaks = seq(2010, 2024, by = 1)) + #reverse y-axis and show each year
  theme_classic() +
  theme(axis.title.x = element_blank(),
                axis.title.y = element_blank()) +
  labs(
    title = "Seasonality Trends in Total Net Weight of Imports")

ggplotly(p) %>%
  layout(
    title = list(size = 20),
    xaxis = list(side = "top"),
    yaxis = list(autorange = TRUE),
    yaxis = list(visible = FALSE) #hide y-axis
    )

```

Note: In the Southern Hemisphere, the seasons are generally as followed: Summer = Dec-Feb, Fall = Mar-May, Winter = Jun-Aug, Spring = Sep-Nov.

#### China

```{r}
#| title: China

# level order so Jan is at the beginning of the y-axis
china <- china %>%
  mutate(month_abb = factor(china$month_abb, levels = c("Jan", "Feb", "Mar", "Apr", "May", "Jun", "Jul", "Aug", "Sep", "Oct", "Nov", "Dec")))

p <- ggplot(china, aes(x=month_abb, y=year)) +
  geom_tile(aes(fill = net_wgt_kgs)) +
  scale_fill_distiller(palette = "RdPu", direction = 1 ,labels = comma) +
  scale_y_reverse(breaks = seq(2010, 2024, by = 1)) + #reverse y-axis and show each year
  theme_classic() +
  theme(axis.title.x = element_blank(),
                axis.title.y = element_blank()) +
  labs(
    title = "China's Seasonality Trends in Total Net Weight of Imports")

ggplotly(p) %>%
  layout(
    title = list(size = 20),
    xaxis = list(side = "top"),
    yaxis = list(autorange = TRUE),
    yaxis = list(visible = FALSE) #hide y-axis
    )

```

Note: In the Southern Hemisphere, the seasons are generally as followed: Summer = Dec-Feb, Fall = Mar-May, Winter = Jun-Aug, Spring = Sep-Nov.

#### India

```{r}
#| title: India

# level order so Jan is at the beginning of the y-axis
india <- india %>%
  mutate(month_abb = factor(india$month_abb, levels = c("Jan", "Feb", "Mar", "Apr", "May", "Jun", "Jul", "Aug", "Sep", "Oct", "Nov", "Dec")))

p <- ggplot(india, aes(x=month_abb, y=year)) +
  geom_tile(aes(fill = net_wgt_kgs)) +
  scale_fill_distiller(palette = "RdPu", direction = 1 ,labels = comma) +
  scale_y_reverse(breaks = seq(2010, 2024, by = 1)) + #reverse y-axis and show each year
  theme_classic() +
  theme(axis.title.x = element_blank(),
                axis.title.y = element_blank()) +
  labs(
    title = "India's Seasonality Trends in Total Net Weight of Imports")

ggplotly(p) %>%
  layout(
    title = list(size = 20),
    xaxis = list(side = "top"),
    yaxis = list(autorange = TRUE),
    yaxis = list(visible = FALSE) #hide y-axis
    )

```

Note: In the Southern Hemisphere, the seasons are generally as followed: Summer = Dec-Feb, Fall = Mar-May, Winter = Jun-Aug, Spring = Sep-Nov.

#### South Africa

```{r}
#| title: South Africa

# level order so Jan is at the beginning of the y-axis
south_africa <- south_africa %>%
  mutate(month_abb = factor(south_africa$month_abb, levels = c("Jan", "Feb", "Mar", "Apr", "May", "Jun", "Jul", "Aug", "Sep", "Oct", "Nov", "Dec")))

p <- ggplot(south_africa, aes(x=month_abb, y=year)) +
  geom_tile(aes(fill = net_wgt_kgs)) +
  scale_fill_distiller(palette = "RdPu", direction = 1 ,labels = comma) +
  scale_y_reverse(breaks = seq(2010, 2024, by = 1)) + #reverse y-axis and show each year
  theme_classic() +
  theme(axis.title.x = element_blank(),
                axis.title.y = element_blank()) +
  labs(
    title = "South Africa's Seasonality Trends in Total Net Weight of Imports")

ggplotly(p) %>%
  layout(
    title = list(size = 20),
    xaxis = list(side = "top"),
    yaxis = list(autorange = TRUE),
    yaxis = list(visible = FALSE) #hide y-axis
    )

```

Note: In the Southern Hemisphere, the seasons are generally as followed: Summer = Dec-Feb, Fall = Mar-May, Winter = Jun-Aug, Spring = Sep-Nov.

#### Uruguay

```{r}
#| title: Uruguay

# level order so Jan is at the beginning of the y-axis
uruguay <- uruguay %>%
  mutate(month_abb = factor(uruguay$month_abb, levels = c("Jan", "Feb", "Mar", "Apr", "May", "Jun", "Jul", "Aug", "Sep", "Oct", "Nov", "Dec")))

p <- ggplot(uruguay, aes(x=month_abb, y=year)) +
  geom_tile(aes(fill = net_wgt_kgs)) +
  scale_fill_distiller(palette = "RdPu", direction = 1 ,labels = comma) +
  scale_y_reverse(breaks = seq(2010, 2024, by = 1)) + #reverse y-axis and show each year
  theme_classic() +
  theme(axis.title.x = element_blank(),
                axis.title.y = element_blank()) +
  labs(
    title = "Uruguay's Seasonality Trends in Total Net Weight of Imports")

ggplotly(p) %>%
  layout(
    title = list(size = 20),
    xaxis = list(side = "top"),
    yaxis = list(autorange = TRUE),
    yaxis = list(visible = FALSE) #hide y-axis
    )

```

Note: In the Southern Hemisphere, the seasons are generally as followed: Summer = Dec-Feb, Fall = Mar-May, Winter = Jun-Aug, Spring = Sep-Nov.
:::

### Revenue (USD \$)

::: panel-tabset
#### All

```{r}
#| title: All

# level order so Jan is at the beginning of the y-axis
merged_all <- merged_all %>%
  mutate(month_abb = factor(merged_all$month_abb, levels = c("Jan", "Feb", "Mar", "Apr", "May", "Jun", "Jul", "Aug", "Sep", "Oct", "Nov", "Dec")))

p <- ggplot(merged_all, aes(x=month_abb, y=year)) +
  geom_tile(aes(fill = primary_value_usd)) +
  scale_fill_distiller(palette = "RdPu", direction = 1 ,labels = comma) +
  scale_y_reverse(breaks = seq(2010, 2024, by = 1)) + #reverse y-axis and show each year
  theme_classic() +
  theme(axis.title.x = element_blank(),
                axis.title.y = element_blank()) +
  labs(
    title = "Seasonality Trends in Total Revenue of Imports")

ggplotly(p) %>%
  layout(
    title = list(size = 20),
    xaxis = list(side = "top"),
    yaxis = list(autorange = TRUE),
    yaxis = list(visible = FALSE) #hide y-axis
    )

```

Note: In the Southern Hemisphere, the seasons are generally as followed: Summer = Dec-Feb, Fall = Mar-May, Winter = Jun-Aug, Spring = Sep-Nov.

#### China

```{r}
#| title: China

# level order so Jan is at the beginning of the y-axis
china <- china %>%
  mutate(month_abb = factor(china$month_abb, levels = c("Jan", "Feb", "Mar", "Apr", "May", "Jun", "Jul", "Aug", "Sep", "Oct", "Nov", "Dec")))

p <- ggplot(china, aes(x=month_abb, y=year)) +
  geom_tile(aes(fill = primary_value_usd)) +
  scale_fill_distiller(palette = "RdPu", direction = 1 ,labels = comma) +
  scale_y_reverse(breaks = seq(2010, 2024, by = 1)) + #reverse y-axis and show each year
  theme_classic() +
  theme(axis.title.x = element_blank(),
                axis.title.y = element_blank()) +
  labs(
    title = "China's Seasonality Trends in Total Revenue of Imports")

ggplotly(p) %>%
  layout(
    title = list(size = 20),
    xaxis = list(side = "top"),
    yaxis = list(autorange = TRUE),
    yaxis = list(visible = FALSE) #hide y-axis
    )

```

Note: In the Southern Hemisphere, the seasons are generally as followed: Summer = Dec-Feb, Fall = Mar-May, Winter = Jun-Aug, Spring = Sep-Nov.

#### India

```{r}
#| title: India

# level order so Jan is at the beginning of the y-axis
india <- india %>%
  mutate(month_abb = factor(india$month_abb, levels = c("Jan", "Feb", "Mar", "Apr", "May", "Jun", "Jul", "Aug", "Sep", "Oct", "Nov", "Dec")))

p <- ggplot(india, aes(x=month_abb, y=year)) +
  geom_tile(aes(fill = primary_value_usd)) +
  scale_fill_distiller(palette = "RdPu", direction = 1 ,labels = comma) +
  scale_y_reverse(breaks = seq(2010, 2024, by = 1)) + #reverse y-axis and show each year
  theme_classic() +
  theme(axis.title.x = element_blank(),
                axis.title.y = element_blank()) +
  labs(
    title = "India's Seasonality Trends in Total Revenue of Imports")

ggplotly(p) %>%
  layout(
    title = list(size = 20),
    xaxis = list(side = "top"),
    yaxis = list(autorange = TRUE),
    yaxis = list(visible = FALSE) #hide y-axis
    )

```

Note: In the Southern Hemisphere, the seasons are generally as followed: Summer = Dec-Feb, Fall = Mar-May, Winter = Jun-Aug, Spring = Sep-Nov.

#### South Africa

```{r}
#| title: South Africa

# level order so Jan is at the beginning of the y-axis
south_africa <- south_africa %>%
  mutate(month_abb = factor(south_africa$month_abb, levels = c("Jan", "Feb", "Mar", "Apr", "May", "Jun", "Jul", "Aug", "Sep", "Oct", "Nov", "Dec")))

p <- ggplot(south_africa, aes(x=month_abb, y=year)) +
  geom_tile(aes(fill = primary_value_usd)) +
  scale_fill_distiller(palette = "RdPu", direction = 1 ,labels = comma) +
  scale_y_reverse(breaks = seq(2010, 2024, by = 1)) + #reverse y-axis and show each year
  theme_classic() +
  theme(axis.title.x = element_blank(),
                axis.title.y = element_blank()) +
  labs(
    title = "South Africa's Seasonality Trends in Total Revenue of Imports")

ggplotly(p) %>%
  layout(
    title = list(size = 20),
    xaxis = list(side = "top"),
    yaxis = list(autorange = TRUE),
    yaxis = list(visible = FALSE) #hide y-axis
    )

```

Note: In the Southern Hemisphere, the seasons are generally as followed: Summer = Dec-Feb, Fall = Mar-May, Winter = Jun-Aug, Spring = Sep-Nov.

#### Uruguay

```{r}
#| title: Uruguay

# level order so Jan is at the beginning of the y-axis
uruguay <- uruguay %>%
  mutate(month_abb = factor(uruguay$month_abb, levels = c("Jan", "Feb", "Mar", "Apr", "May", "Jun", "Jul", "Aug", "Sep", "Oct", "Nov", "Dec")))

p <- ggplot(uruguay, aes(x=month_abb, y=year)) +
  geom_tile(aes(fill = primary_value_usd)) +
  scale_fill_distiller(palette = "RdPu", direction = 1 ,labels = comma) +
  scale_y_reverse(breaks = seq(2010, 2024, by = 1)) + #reverse y-axis and show each year
  theme_classic() +
  theme(axis.title.x = element_blank(),
                axis.title.y = element_blank()) +
  labs(
    title = "Uruguay's Seasonality Trends in Total Revenue of Imports")

ggplotly(p) %>%
  layout(
    title = list(size = 20),
    xaxis = list(side = "top"),
    yaxis = list(autorange = TRUE),
    yaxis = list(visible = FALSE) #hide y-axis
    )

```

Note: In the Southern Hemisphere, the seasons are generally as followed: Summer = Dec-Feb, Fall = Mar-May, Winter = Jun-Aug, Spring = Sep-Nov.
:::

```{r}
#closing the revenue tabset
```
:::::

```{r}
#closing column 2's section
```
:::::::

```{r}
#closing the layoutn-col section
```

# Data

## Row {height="100%"}

::: panel-tabset
### Dataset

```{r}

#| title: Dataset
#| echo: false

datatable(b_wool_2v,
          filter = "top",
          options = list(
            pageLength = 30
          )) %>%
  formatRound(columns = c("net_wgt_kgs", "net_wgt_lbs", "primary_value_usd"), digits = 2) 

```

### Data Dictionary

```{r}

#| title: Data Dictionary
#| echo: false

datatable(data_dict,
          filter = "top",
          options = list(
            pageLength = 30
          ))

```
:::

# Takeaways

::: panel-tabset
## Top Importer

```{r}

#| out.width: "100%"

#1. Top Importer

#creating column to highlight just South Africa
importer <- importer %>%
  mutate(top_imp = if_else(country == "South Africa", "yes", "no"))

#define colors
color_importer <- c("yes" = "#88419d", "no" = "gray40")

#bar chart in plotly
top_imp <- plot_ly(
  data = importer,
  x = ~country,
  y = ~total_netwgt_kgs,
  type = "bar",
  color = ~top_imp,
  colors = color_importer,
  text = ~paste0(format(total_netwgt_kgs, big.mark = ","), "<br>", #value I want to show with commas
    paste0("($", format(total_value_usd, big.mark = ","), " USD)")),
  textposition = "outside", #where I want to put label
  textfont = list(weight = "bold"), 
  cliponaxis = FALSE, #prevents text label from being clipped
  showlegend = FALSE # hides the legend
) %>%
  layout(
    title = "1. South Africa was the top importer of Lesotho’s Basotho wool by total net weight (kg).",
    margin = list(t = 50), #adds px of padding to the top
    yaxis = list(visible = FALSE) #hide y-axis
    )

top_imp

```

Note: China's net weight values from 2016-2017 were listed as estimates.

## Biggest Year

```{r}

#| out.width: "100%"

#2. Biggest Year

#creating column to highlight just 2020
top_year <- top_year %>%
  mutate(top_yr = if_else(year == "2020", "yes", "no"))


#define colors
color_year <- c("yes" = "#88419d", "no" = "gray40")

#bar chart in plotly
top_yr <- plot_ly(
  data = top_year,
  x = ~year,
  y = ~total_netwgt_kgs,
  type = "bar",
  color = ~top_yr,
  colors = color_year,
  text = ~paste0(format(total_netwgt_kgs, big.mark = ","), "<br>", #two line label
    ifelse(wgt_pctchg > 0,
           paste0("<span style='color:#2166ac;'>", "(", wgt_pctchg, "%)", "</span>"), #if yes
           paste0("<span style='color:#b2182b;'>", "(", wgt_pctchg, "%)", "</span>") # if no
           )),
  textposition = "outside", #where I want to put label
  textfont = list(weight = "bold"), 
  showlegend = FALSE
) %>%
  layout(
    title = list(
      text = "2. 2020 was the biggest year for Lesotho’s Basotho wool trade, with a +166% boost in the amount of wool traded.",
    subtitle = list(
      text = "Due to the governmental restriction on wool exports between 2018-2019, the net weight of Lesotho’s Basothol wool trade decreased by -72% in 2018 and increased by +47% in 2019.")),
    yaxis = list(visible = FALSE) #hide y-axis
    )

top_yr

```

Note: In 2018, Lesotho's government restricted wool trade with South Africa, resulting in a 72% decrease in the net weight of imports for the year.

## Most Revenue

```{r}

#| fig-height: 25
#| out.width: "100%"

#creating column to highlight just 2023
revenue <- most_revenue %>%
  mutate(most_rev = if_else(year == "2023", "yes", "no"))

#define colors
color_year <- c("yes" = "#88419d", "no" = "gray40")

#bar chart in plotly
top_rev <- plot_ly(
  data = revenue,
  x = ~year,
  y = ~total_value_usd,
  type = "bar",
  color = ~most_rev,
  colors = color_year,
  text = ~paste0("$", format(total_value_usd, big.mark = ","), "<br>", #two line label
    ifelse(value_pctchg > 0,
           paste0("<span style='color:#2166ac;'>", "(", value_pctchg, "%)", "</span>"), #if yes
           paste0("<span style='color:#b2182b;'>", "(", value_pctchg, "%)", "</span>") # if no
           )),
  textposition = "outside", #where I want to put label
  textfont = list(weight = "bold"), 
  showlegend = FALSE
) %>%
  layout(
    title = list(
    text = "3. Lesotho received the most revenue in 2023 (with a +21% jump in $$ made between 2022-2023).",
    yref = "container", # Ensures margin expands relative to the outer container
    automargin = TRUE),   # Automatically adjusts margins to prevent overlap),
  margin = list(t = 50), # adds pixels of padding to the top
  yaxis = list(visible = FALSE) #hide y-axis
    )

top_rev
```

Note: In 2018, Lesotho's government restricted wool trade with South Africa, resulting in a 21% decrease in revenue for the year.

## Busiest Season

```{r}

#| out.width: "100%"

#creating column to highlight just Spring
season <- busy_season %>%
  mutate(top_season = if_else(sh_season == "Southern Hemisphere Spring", "yes", "no"))

#define colors
color_season <- c("yes" = "#88419d", "no" = "gray40")

#bar chart in plotly
top_ssn <- plot_ly(
  data = season,
  x = ~sh_season,
  y = ~total_netwgt_kgs,
  type = "bar",
  color = ~top_season,
  colors = color_season,
  text = ~paste0(format(total_netwgt_kgs, big.mark = ","), "<br>", #value I want to show with commas
    paste0("($", format(total_value_usd, big.mark = ","), " USD)")),
  textposition = "outside", #where I want to put label
  textfont = list(weight = "bold"),
  cliponaxis = FALSE, #prevents text label from being clipped
  showlegend = FALSE # hides the legend
) %>%
  layout(
    title = list(
      text = "4. Spring (Sep-Nov) was the busiest season for imports (by net weight) and for revenue.",
      yref = "container", # Ensures margin expands relative to the outer container
      automargin = TRUE),   # Automatically adjusts margins to prevent overlap
    margin = list(t=20),
    yaxis = list(visible = FALSE) #hide y-axis
    )


top_ssn
```

Note: In the Southern Hemisphere, the seasons are generally as followed: Summer = Dec-Feb, Fall = Mar-May, Winter = Jun-Aug, Spring = Sep-Nov.
:::
